% The \phantomsection command is needed to create a link to a place in the document that is not a
% figure, equation, table, section, subsection, chapter, etc.
%
% When do I need to invoke \phantomsection?
% https://tex.stackexchange.com/questions/44088/when-do-i-need-to-invoke-phantomsection
\phantomsection


% Multiple-language document - babel - selectlanguage vs begin/end{otherlanguage}
% https://tex.stackexchange.com/questions/36526/multiple-language-document-babel-selectlanguage-vs-begin-endotherlanguage

\chapter[Discussion]{Discussion: Applications versus Measures}\label{sec:discussion}


\begin{flushright}
 
\end{flushright}


{Trajectory data can have several formats. Depending on the format and the application requirements, different trajectory analysis and mining methods will be needed, and so different similarity measures can be applied. For applications that use raw GPS data, as trajectories of taxis, buses, or cars, with the intend to detect, for instance, traffic conditions or traffic jams, the most appropriate measures are UMS and DTWa. UMS is robust for trajectories with different sampling rates or different distances between trajectory points (the case when a trajectory varies the speed in a city), because instead of using a radius around each trajectory point to find the similar trajectories in the spatial neighbourhood, it uses ellipses between every two trajectory points, and the size of the ellipses is dinamically defined based on the distance between two trajectory points. UMS is not the best measure in highly sampled trajectories, where the ellipses are very small, and in this case DTWa is  a good choice.}

{For applications that use GPS trajectories annotated only with stops or where the moves are not important, or trajectories extracted from social media data, which are more sparse and that do not have moves, the best measure is MSM. MSM is useful in applications where one is interested in finding users that visit the same places, at similar times, but where the order of the visits is not important. In tourism applications where the analyst wants to find similar tourist trajectories to either predict or to recommend the next place to be visited, MSM is not appropriate because it ignores the order. When the sequence of the visited places is important, even when the details about the moves are not, SMSM is more appropriate, because it considers the order of the stops.}

{For dealing with GPS trajectories enriched with both stops and moves, and the spatial, temporal or semantic characteristcs of both stops and moves are important, SMSM is the most appropriate measure. In a tourism application, for instance, where the tourist has a time constraint to visit a city, a sequence of visits can be recommended based on the similarity analysis of other tourists that visited the same city. SMSM is also robust in applications that focus on the most similar paths or popular routes between stops.}

{It is important to emphasize that in applications where the spatial movement of the moves is important, i.e., the raw trajectory points, SMSM can use UMS for the move similarity when trajectories have low sampling rate and DTW when trajectories have high sampling rate.}
